Bricking up backdoors in Intrusion Detection Systems

### 2019-09-16 paper/paper.tex

There have been several works with the aim of increasing robustness of decision trees against attacks. \cite{biggio_bagging_2011} proposed a defense mechanism against poisoning that uses bagging to try to minimize the influence of a backdoor that is introduced in the training dataset. Their method is applicable to \glspl{dt}. However, this approach cannot protect if a trained model is obtained from another (untrusted) party in which the other party might potentially have introduced a backdoor, which is the use case considered in this work. \cite{chen_robust_2019} developed a method to train \glspl{dt} with a tunable parameter that trades off accuracy against robustness against evasion attacks. \cite{russu_secure_2016} makes SVMs robust against evasion attacks and outline a possibility to also apply it to \glspl{dt} and \glspl{rf}.
%\todo{Max: Unnecessary or should be moved to Related Work?}

Pruning for neural networks has been proposed
%in the last century
as a method to simplify large neural networks \cite{sietsma_neural_1988}.
Pruning as a defense for neural networks against poisoning has emerged recently \cite{gu_badnets:_2017}. They proposed pruning as a defense mechanism against backdoored \glspl{cnn} and show that by removing infrequently used neurons from the last convolutional layer, potential backdoors can be removed. The rationale behind this is that some neurons specialize processing the regular samples while others focus on the backdoor.
To our knowledge, these pruning defences have been applied to \glspl{cnn} but not to \glspl{mlp}, which are commonly used for \glspl{ids} \cite{meghdouri_analysis_2018}. Altheugh various pruning techniques have been proposed for \glspl{dt} in the last decades \cite{esposito_comparative_1997} with the aim of simplifying trees that overfit on the training data, pruning has not yet been investigated for its suitability for defending against backdoors for \glspl{dt} and \glspl{rf}.

>>>>

There have been several works with the aim of increasing robustness of decision trees against attacks. \cite{biggio_bagging_2011} proposes a defense mechanism against poisoning that uses bagging to try to minimize the influence of a backdoor that is introduced in the training dataset. The method is applicable to \glspl{dt}. However, this approach cannot protect if a trained model is obtained from another (untrusted) party in which the other party might potentially have introduced a backdoor, which is the use case considered in this work. \cite{chen_robust_2019} develops a method to train \glspl{dt} with a tunable parameter that trades off accuracy against robustness against evasion attacks. \cite{russu_secure_2016} makes SVMs robust against evasion attacks and outlines a possibility to also apply it to \glspl{dt} and \glspl{rf}.
%\todo{Max: Unnecessary or should be moved to Related Work?}

Pruning for neural networks has been proposed
%in the last century
as a method to simplify large neural networks \cite{sietsma_neural_1988}.
Pruning as a defense for neural networks against poisoning has emerged recently \cite{gu_badnets:_2017}. They proposed pruning as a defense mechanism against backdoored \glspl{cnn} and show that by removing infrequently used neurons from the last convolutional layer, potential backdoors can be removed. The rationale behind this is that some neurons specialize processing the regular samples while others focus on the backdoor.
To our knowledge, these pruning defences have been applied to \glspl{cnn} but not to \glspl{mlp}, which are commonly used for \glspl{ids} \cite{meghdouri_analysis_2018}. Although various pruning techniques have been proposed for \glspl{dt} in the last decades \cite{esposito_comparative_1997} with the aim of simplifying trees that overfit on the training data, pruning has not yet been investigated for its suitability for defending against backdoors for \glspl{dt} and \glspl{rf}.
